---
title: "Data Wrangling I"
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

## Import some data

I want to import `FAS_litters.csv`, 

```{r}
litters_df = read_csv("data/FAS_litters.csv")
```

Dataset imported. Now we want better names.

```{r}
names(litters_df)

litters_df = janitor::clean_names(litters_df)
```

Now we have better names (snake_case). Lets look at the dataset

```{r}
litters_df

head(litters_df, 20)
tail(litters_df)
```

One used a lot is:
Eval set to false so as not to cause issues when knitting

```{r, eval = FALSE}
view(litters_df)
```

Here's skim

```{r}
skimr::skim(litters_df)
```

## Arguments in `read_csv`

```{r}
litters_df = 
  read_csv(
    "data/FAS_litters.csv",
    skip = 5,
    col_names = FALSE,
    na = "Low8")
```

## Parsing columns

```{r}
litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD18 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)
```

Can also specify individuals columns type no need to list every column when only on returns a parse error

## Reading From Excel

Reading MLB data

```{r}
mlb11_df = read_excel("data/mlb11.xlsx")
```

Now LotR Words is next

```{r}
fellow_df = read_excel("data/LotR_Words.xlsx", range = "B3:D6")
```

## Read a SAS file

This is where we tried to read a SAS file

```{r, eval = FALSE}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")
```

## Why to never use `read.csv`

```{r, eval=FALSE}
litters_df_base = read.csv("data/FAS_litters.csv")
```

This does not print out as a tibble! (We like `tibble` its nice) Also read.csv has some old issues in how it reads in variables


## How to export

there's a way!

```{r}
write_csv(fellow_df, "data/fellowship_words.csv")
```

